\newpage
\section{Group Members Contribution}
\par
Throughout the project lifecycle, the team conducted multiple meetings to ensure that the project was executed successfully. The initial stages involved selecting a pertinent subject and devising an appropriate implementation strategy. The team engaged in extensive deliberations to determine the project requirements and defined all relevant classes and entities. Subsequently, tasks were assigned to individual team members using the Trello platform. Throughout the project duration, each team member fulfilled specific responsibilities that were critical to the success of the endeavor. Through collaborative efforts, the team developed a dependable and robust system that met the expectations of both users and stakeholders. Their commitment to working together allowed for effective completion of various tasks, leading to the successful execution of the project. In the following paragraphs, a detailed account of each team member's responsibilities is provided.
% For each group member, describe in detail the contribution to the project.

\begin{description}
	\item[Reihaneh Baghishani] She created Sequence Diagrams and built entities like Drug for the project. She implemented servlets, JSPs, and RESTful APIs using Spring Boot framework, designed DAO and service layers, and created filters to enhance the functionality of Drugs and Materials modules. Additionally, she contributed to exception handling, documented APIs, modified the designs to conform to RESTful API standards, and helped implement certain methods for the Drug and Material entities.

	\item[Ali Erfanian Omidvar] He had a diverse set of responsibilities, such as defining the system structure and creating a response helper for APIs. Additionally, he was responsible for fixing any issues related to the relationship between entities and creating a security service for the system. He also contributed to refactoring the order entity, service, and repository and created a log service to ensure system accuracy. Finally, he reviewed the merge request on git and refactored the URLs.
 
	\item[Irem Goksu Celik] In her role, she was responsible for implementing the supplier and login entity and repository. Additionally, she developed the order CRUD API and prepared the class diagram. She also contributed to the implementation of storage reports for the system.
 
	\item[Hamideh Haeri] Her role encompassed various responsibilities, including creating the Entity Relationship diagram, defining the attributes and methods of the Pharmacy entity, and developing the Receipt API. She was also responsible for creating the project document and fixing API issues, as well as adding validation checks to ensure system accuracy. Additionally, she contributed to the implementation of some methods in the User module.
 
	\item[Ferdos Hajizadeh Chavari] Her role encompassed various tasks, such as implementing and designing the material entity and repository, developing the drug API, and implementing the payment method. Additionally, she was responsible for editing the project document to ensure system accuracy.
 
	\item[Hossein Hosseinpour] As part of his role, he was responsible for defining the attributes and methods of the Storage entity and developing the Pharmacy API. He also created the sequence diagram for the Pharmacy save API and was responsible for fixing any related API issues and adding validation checks to the system. Additionally, he contributed to the implementation of some methods in the User module.

   \item[Gulce Sirvanci] She had multiple responsibilities, including implementing the user entity and repository, supplier repository, and supplier CRUD API. Furthermore, she was responsible for the implementation of storage reports for the amount of each drug and material, as well as the threshold parameters.

   \item[Ali Tahvildari] He had a diverse set of responsibilities, which included designing and implementing the order entity and fixing any related issues. He also collaborated with others to implement Swagger and design and implement the wireframe for the system layout and contributed to the implementation of the material and user API methods, as well as some methods in the User module.

   \item[Mohammad Torabi] As part of his responsibilities, he created the Receipt entity and implemented the Storage module of the back-end system using Spring Boot. To achieve this, he had to design and implement the API, repository, and service layers for the Storage entity. In addition, he contributed to the implementation of some methods in the User and Receipt modules and edited the project documentation.

\end{description}
