\documentclass{ceurart}

\usepackage{acronym}
\usepackage{subcaption}

\renewcommand{\acffont}[1]{\textsl{#1}}


%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% Rights management information.
%% CC-BY is default license.
\copyrightyear{2023}
\copyrightclause{Copyright for this paper by its authors.\\
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

%%
%% This command is for the conference information
\conference{``Search Engines'', course at the master degree in ``Computer Engineering'', Department of Information Engineering, and at the master degree in ``Data Science'', Department of Mathematics ``Tullio Levi-Civita'', University of Padua, Italy. Academic Year 2022/2023}

%%
%% The "title" command
\title{SEUPD@CLEF: Team <Semicolon>}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
\author[1]{Reihaneh Baghishani}[%
email=reihaneh.baghishani@studenti.unipd.it
]

\author[1]{Irem Goksu Celik}[%
email=iremgoksu.celik@studenti.unipd.it
]

\author[1]{Hamideh Haeri}[%
email=hamideh.haeri@studenti.unipd.it
]

\author[1]{Ferdos \textcolor{black}{Hajizadeh} Chavari}[%
email=ferdos.hajizadehchavari@studenti.unipd.it
]

\author[1]{Hossein Hosseinpour}[%
email=hossein.hosseinpour@studenti.unipd.it
]

\author[1]{Ali Tahvildari}[%
email=ali.tahvildari@studenti.unipd.it
]

\author[1]{Mohammad Torabi}[%
email=mohammad.torabi@studenti.unipd.it
]

\address[1]{University of Padua, Italy}


%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  In this paper, we present a search engine, focusing on efficient indexing, sanitization, and retrieval of relevant documents. We implemented a system that first checks if the input documents are sanitized and then proceeds with the sanitization process if required, storing the cleaned documents in a separate directory. The system then indexes the documents using a custom DirectoryIndexer that leverages an NGramAnalyzer and a similarity measure based on the BM25 algorithm. The DirectoryIndexer also uses a parser to extract meaningful information from the documents. The system is designed to handle a large number of documents, with a specific focus on the English language. It supports both single-line and multi-line document formats and can easily adapt to different input and output folders. The search engine also provides a searching functionality that accepts a set of queries and returns a run file containing evaluation measures to assess the relevance of the retrieved documents. Our search engine aims to facilitate efficient information retrieval and improve the overall user experience while working with academic documents.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
  Search Engine \sep
  Academic Purposes \sep
  Sanitization \sep
  Indexing \sep
  BM25 Algorithm \sep
  Parser \sep
  Information retrieval \sep
\end{keywords}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle


\input{section/introduction}

\input{section/methodology}

\input{section/setup}

\input{section/results}

\input{section/conclusion}





%% Define the bibliography file to be used
\bibliography{bibliography,proceedings}

\input{acronyms}


\end{document}
